Our team will need lab space in order to work on our rover. We will also need access to a rover/drone cage for safe testing of the rover. This testing ground is already present in the senior design labs we are provided.

We will require hardware components necessary for building an indoor navigation rover. This includes and is not limited to processors, power supplies and sensors. Furthermore, our team needs a place to store our rover, components, and related tools. There are black bins located in the senior design labs already that can be reserved, which covers tools and components. However, the rover is too large to be stored in the bin.

Already present in the lab are the retired UTARI rovers. This provides our team with a lot of starting materials. The rover will still require some components we do not have and these we will have to be purchase. Cannibalizing the UTARI rover and assembling the new rover will require tools, such as screwdrivers, wire cutters, soldering iron, wires, and more. Most of these tools are available to us in the senior design labs. Our team might need access to a MakerSpace to 3D print parts to hold or support components inside the rover. Further needs and and other equipment will be put here.

%What lab space, testing grounds, makerspaces, etc. will you need to complete the project? Will you require any specific equipment, and if so, where will you get it (borrow, lease, purchase, outsource, already present in the lab, etc.). This section should occupy 1/2 page.