In the modern education system today, most students don't have the opportunity to engage with challenges involving autonomous navigation. As technology can provide quick answers, it is important to equip students with interactive experiences to promote critical thinking and problem solving skills.
\\\\
To provide interactive learning, our team will develop the "Roam\_Bot", an Autonomous Indoor Rover. This rover will navigate through complex environments without the use of GPS systems. Using advanced sensors, the rover can provide abstracted information to test pathfinding algorithms in a dynamic environment.
\\\\
By creating allowing students to interact and observe with the "Roam\_Bot", we can bridge the gap between theoretical knowledge and practical application. As students test their algorithms on this device, they will develop a deeper understanding of robotics and real-time systems. Overall, our robot will equip students to adapt to future technological innovations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INSTRUCTIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The problem statement defines the "Why" of the project. This is the higher purpose, or the reason for the project's existence. This section should avoid mentioning implementation details, and focus more on what the current problem is and what would be gained if the problem were to be solved. In short, the is the reason that you are going to be working on something, not the method(s) that you will be employing.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% EXTRA
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Fire safety regulations have been implemented in every day activity.
% Fire safety regulations has a main focus on informing and helping non-disabled people during such circumstances. Our robot aims to help those that are disabled such as visually impaired, deaf, and many others that has something impairing their day to day life. With our robot helping those that need extra assistance, less people would need to stay in the dangerous area and result in less casualties in such emergencies.
% for wheel chair users the robot could throw out a slide so that people can go down the stairs  