% Each of us tal about what we are good at based on what we ae taking responsibilitiy for within the rover project. Point of contect for sponser we will just say conly is our sponser  so who in our team is our point of contect? Raya is currently scrm master right? but we agreed it would swap around?? Who are stakeholders. we hold stake right? university for paying for it? !!!!!
% 4316_Fa24_TR11_Project_Charter.mp4 time 20:50

As of now, Raya Sultan is assigned as the SCRUM master, and () is our product owner. These are subject to change over time. Our point of contact from the sponsor side will be Christopher Conly, from the team side it is Andrew Howard. At present, the university is the stakeholder of the project, given it is an educational project to aid other students in their real-time understanding of different navigation algorithms. Our sponsor is Christopher Conly.

Abubakar Kassim, due to his experience in software engineering, is responsible for programming and simulating various navigation algorithms. 

Madison Gage, due to her experience building an indoor rover, focus on designing and assembling the indoor rover.

Christopher Davis, due to his experience with embedded systems will focus on designing and assembling the indoor rover.

Raya Sultan, due to her graphics as well as engineering skills, will focus on drawing up schematics and diagrams, as well as assist in assembling the motor.

Andrew Howard, with his experience in digital systems, will focus on interfacing the hardware of the indoor rover with abstract software.

%Who are the stakeholders of the project? Who will be the point of contact from the sponsor or customer side? Who are the team members, and what will be their areas of responsibility? Will your team maintain the product owner and scrum master for the whole project, or will that role change periodically? This section should occupy 1/2 - 1 full page.